Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-25 cav2017/cav2017.tex
wordings

Linear Time Invariant (LTI) models represent a broad class of dynamical
systems with significant impact in numerous application areas as in the life
sciences, robotics, and engineering~\cite{astrom1997computer,Franklin15}. 
Synthesis of controllers for LTI models is broadly investigated, however the
use of digital control architectures adds new challenges due to the effects
of finite-precision arithmetic, time discretization, and quantization noise,
which are typically introduced by Analogue-to-Digital (ADC) and
Digital-to-Analogue (DAC) conversion.  While research on digital control is
well developed~\cite{astrom1997computer}, automated and sound control
synthesis is challenging, particularly when the synthesis objective goes
beyond classical stability or tracking requirements.  Beyond stability,
recently reachability tools have been developed~\cite{FLD+11,Fre05}, however
they have not been employed towards control synthesis.  The problem of
safety is an important one, since the synthesis of a stable controller does
not ensure that the system will not transitively visit an unsafe state which
may result in an unrecoverable failure.

In this work, we propose the synthesis of \emph{safe} control algorithms for
LTI models taking into consideration the continuous dynamics of the plant, 
alongside the discrete dynamics of the controller and the effects of its 
implementation, as well as the hybrid elements that relate them.  
%% In this paper, we synthesize controllers for hybrid
%% closed-loop systems, i.e., software-implemented embedded controllers along
%% with a model of their physical environment (the plant), that are
%% \emph{safe}.
Due to the complexity of such systems, in this work we focus 
on linear models with known  implementation features (e.g., number of bits, fixed-point
arithmetic). We specify the safety requirement over the state space. This is a property often 
overlooked in feedback control synthesis, but which plays an important role 
in real-world systems.

>>>>

Linear Time Invariant (LTI) models represent a broad class of dynamical
systems with significant impact in numerous application areas as in the life
sciences, robotics, and engineering~\cite{astrom1997computer,Franklin15}. 
Synthesis of controllers for LTI models is broadly investigated, however the
use of digital control architectures adds new challenges due to the effects
of finite-precision arithmetic, time discretization, and quantization noise,
which are typically introduced by Analogue-to-Digital (ADC) and
Digital-to-Analogue (DAC) conversion.  While research on digital control is
well developed~\cite{astrom1997computer}, automated and sound control
synthesis is challenging, particularly when the synthesis objective goes
beyond classical stability.  There are recent methods for verifying more
general reachability properties of a given controller~\cite{FLD+11,Fre05}. 
However, these methods have not been generalized to control synthesis. 
We~remark that a synthesis algorithm that guarantees satability does not
ensure safety: the system might transitively visit an unsafe state that
results in an unrecoverable failure.

We propose a novel algorithm for the synthesis of control algorithms for LTI
models that are guaranteed to be both stable and safe, considering both the
continuous dynamics of the plant and the finite-precision discrete dynamics
of the controller, as well as the hybrid elements that connect them.
%
%% In this paper, we synthesize controllers for hybrid
%% closed-loop systems, i.e., software-implemented embedded controllers along
%% with a model of their physical environment (the plant), that are
%% \emph{safe}.
%
Due to the complexity of such systems, we focus on linear models with known
implementation features (e.g., number of bits, fixed-point arithmetic). 
We~expect a safety requirement given as a reachability property.  Safety
requirements are frequently overlooked in conventional feedback control
synthesis, but play an important role in systems engineering.
